Vragenlijst thesis evaluatie

### 2015-08-08 doc/template/chap-4.tex
vanalles

The formalisation of the FlipIt game with delay relies on some value  \textit{d} that represents the time needed to infect a sufficient number of nodes in a network after the initial infection. This chapter provides the reader with more insight on how to calculate the value of this parameter \textit{d}.  \\

The  spreading of malware has already been extensively researched. Because of the many different types of propagation it is hard to define a single model that can model all of them. Modelling the spread of malware depends on two key factors: the method used for the propagation and the graph of the network where the malware will spread itself. \\
Viruses and worms are the types of malware that are the most researched. Since the spreading of viruses requires human interaction, their propagation delay is depending on (hard to predict) human behaviour. Worms on the other hand, spread without human intervention, and their propagation is therefore easier to model. Since the purpose of this chapter is only to illustrate how a delay can be calculated, we will limit the presentation to propagation models of worms. \\

The overview of this chapter will be as follow: Section \ref{methodsofpropagation} presents an overview of the most frequently used propagation methods by worms. These propagation methods will be covered by different kinds of models in section \ref{modelsforpropagation} that presents models to determine the time a worm needs to infect a sufficient number of nodes. These results can be used for the completion of parameter \textit{d}. Finally, in section \ref{eigenmatrixmethode},  we introduce an easy method to calculate the delay of the propagation of a worm. % Different kind of graphs to model a computer network are introduced.

@@

In the context of malware propagation, there are two kinds of APT's. First, there are APT's that launch an attack on just one target node of a network. The mechanism these APT's use to propagate malware is the dropper mechanism. The dropper is the initial attack vector that compromises the single targeted node of the system. The second kind of APT's target multiple victims. These APT's also use a dropper mechanism but have an additional mechanism for self-propagation in order to propagate themselves to the multiple targeted nodes of the system. If the APT uses virus spreading, the virus infects one node on the network and has to wait for human interaction to spread. So the spreading speed depends on the human interaction, and modelling virus propagation therefore requires modelling human behaviour. If an APT uses a worm propagation method it will spread by itself after it has been dropped on the network. Given the additional complexity of incorporating the human factor in a spreading method and that this chapter is merely meant as illustration on calculating the delay for use in the game theoretic approach, we will limit the presentation to worm propagation models for APT's. \\

>>>>

The formalisation of the FlipIt game with a delay relies on some value  \textit{d} that represents the time needed to infect a sufficient number of nodes in a network after the initial infection. This chapter provides the reader with more insight on how to calculate the value of this parameter \textit{d}.  \\

The  spreading of malware has already been extensively researched. Because of the many different types of propagation methods it is hard to define a single model that can model all of them. Modelling the spread of malware depends on two key factors: the method used for the propagation and the graph of the network in which the malware will spread itself. \\
Viruses and worms are the types of malware that are the most researched. Since the spreading of viruses requires human interaction, their propagation delay depends on (hard to predict) human behaviour. Worms on the other hand, spread without human intervention, and their propagation is therefore easier to model. Since the purpose of this chapter is only to illustrate how a delay can be calculated, we will limit this chapter to propagation models of worms. \\

The overview of this chapter will be as follows: Section \ref{methodsofpropagation} presents an overview of the most frequently used propagation methods by worms. These propagation methods will be covered by different kinds of models in section \ref{modelsforpropagation} presents models to determine the time a worm needs to infect a sufficient number of nodes. These results can be used for the completion of parameter \textit{d}. \todo{wat wordt er met de vorige zin bedoeld?} Finally, section \ref{eigenmatrixmethode}, introduces an easy method to calculate the delay of the propagation of a worm. % Different kind of graphs to model a computer network are introduced.

@@

In the context of malware propagation, there are two kinds of APT's. First, there are APT's that launch an attack on just one target node of a network. The mechanism these APT's use to propagate malware is the dropper mechanism. The dropper is the initial attack vector that compromises the single targeted node of the system. The second kind of APT's target multiple nodes. These APT's also use a dropper mechanism but have an additional mechanism for self-propagation in order to propagate themselves to the multiple targeted nodes of the system. If the APT uses virus spreading, the virus infects one node on the network and has to wait for human interaction to spread. As such the spreading speed depends on the human interaction, and modelling virus propagation therefore requires modelling human behaviour. If an APT uses a worm propagation method it will spread by itself after it has been dropped on the network. Given the additional complexity of incorporating the human factor in a spreading method and that this chapter is merely meant as illustration on calculating the delay for use in the game theoretic approach, this chapter will be limited to worm propagation models for APT's. \\
